### 2016-11-20 report/survey.tex
Tiny change to survey.

The

>>>>

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}.
\begin{savenotes}
	\begin{table}[htb]
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
			columns/Arch./.style={string type},
			columns/Free/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=\footnote{##1}}
			},
		]{platforms.csv}
	\end{table}
\end{savenotes}

\bibliographystyle{acm}
\bibliography{drp}
